Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-07 R0V0.tex
Erased the diagonal dominant class of matrices. Investigate weak coupling for diagonal dominant matrices.

Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}. If the matrix $F$ has some structure on its diagonal, then the negative definiteness can be shown using a the optimization method proposed in \cite{AhmadiHall2016}.

@@

The set of dd (resp. sdd) matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $DD_h$ (resp. $SDD_h$). Denote the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$, i.e.,
\begin{subequations}
		\begin{equation}\label{eq:}
			\mathbf{DD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=UDU, D\in DD_h\}
		\end{equation}
		\begin{equation}\label{eq:}
			\mathbf{SDD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=UDU, D\in SDD_h\}
		\end{equation}
\end{subequations}

The MI~\eqref{eq:MIF} can be casted into the following second-order cone programming
\begin{subequations}
\begin{equation}\label{eq:DSOS}
\begin{array}{rl}
SDSOS_l:=\underset{}{\min} & t \\
\text{subject to} &  -F_l\in\mathbf{SDD}(U_l)\;,
\end{array}
\end{equation}
which consists of verifying the feasibility $-F_l\in\mathbf{SDD}(U_l)$, where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
\begin{equation}
\begin{array}{rcl}
	U_0&=&\ I_h\\
	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
\end{array}
\end{equation}
\end{subequations}

>>>>

Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}. If the matrix $F$ has some structure on its diagonal, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.

@@

The set of scalable diagonally dominant matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $SDD_h$. Let
		\begin{equation}\label{eq:}
			\mathbf{SDD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=UDU, D\in SDD_h\}
		\end{equation}
be the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$. If the MI~\eqref{eq:MIF} can be casted into the following second-order cone programming
\begin{subequations}
\begin{equation}\label{eq:DSOS}
\begin{array}{rl}
SDSOS_l:=\underset{}{\min} & t \\
\text{subject to} &  -F_l\in\mathbf{SDD}(U_l)\;,
\end{array}
\end{equation}
which consists of verifying the feasibility $-F_l\in\mathbf{SDD}(U_l)$, where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
\begin{equation}
\begin{array}{rcl}
	U_0&=&\ I_h\\
	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
\end{array}
\end{equation}
\end{subequations}
